My title

### 2024-03-28 paper/paper.qmd
removed unused literature and update paper data table

>>>>

For the analysis, we retrieved the following data as described in @tbl-use-var.

| Variable | New Name   | Description                     | Example |
|----------|------------|---------------------------------|---------|
| sex      | sex        | Respondent's gender             | Female  |
| age      | age        | Respondent's age                | 25      |
| HEALTH   | health     | Respondents' health condition   | Good    |
| SATHEALT | AGE        | The age of the respondents      | 23      |
| PHYSHLTH | Phys_Health| Days of Respondents' physical health being not good   | 15    |
| MNTLHLTH | Ment_Health| Respondents' mental health      | MALE    |

: Source data retrieved from GSS {#tbl-use-var}
